The Astropy Project

### 2017-10-27 main.tex
typo

Packaged versions of \astropy are also available for several
operating systems that are managed by a system's package manager,
including Debian, Ubuntu, Fedora, Gentoo, Arch Linux, Mac OS X (e.g.,
via brew, macports or fink) and FreeBSD.  However, on occasion these packages
may be outdated compared with the latest stable release of \astropy accessible
from the PyPI. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for the three majot platforms.
% * <mattwcraig@gmail.com> 2017-10-27T07:16:27.310Z:
% 
% > re-built binary conda packages
% Feel free to remove if this is too detailed. I do think the available of the whole ecosystem across all platforms has helped speed its adoption.
% 
% ^.

>>>>

Packaged versions of \astropy are also available for several
operating systems that are managed by a system's package manager,
including Debian, Ubuntu, Fedora, Gentoo, Arch Linux, Mac OS X (e.g.,
via brew, macports or fink) and FreeBSD.  However, on occasion these packages
may be outdated compared with the latest stable release of \astropy accessible
from the PyPI. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for the three major platforms.
% * <mattwcraig@gmail.com> 2017-10-27T07:16:27.310Z:
% 
% > re-built binary conda packages
% Feel free to remove if this is too detailed. I do think the available of the whole ecosystem across all platforms has helped speed its adoption.
% 
% ^.
